Precise Data Flow Analysis\\in the Presence of Correlated Method Calls

### 2014-12-18 content/impl.tex
add missing comma

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The complexity proof for the IDE algorithm requires the implementation of the micro-functions
to be \textit{efficient} according to the following criteria:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
We prove that the micro-functions for the correlated-call analysis satisfy these
criteria if we consider the number of correlated-call receivers $R$ and the
number of run-time types $T$ constant
(i.e. the operations on micro-functions are allowed to use time that is $O(RT)$,
but constant with respect to $E$ and $D$).

>>>>

Both the IFDS and IDE algorithms have been proven
to run in $O(ED^3)$ time~\cite{reps1995precise,sagiv1996precise},
where $E$ is the number of edges in the (non-exploded) supergraph, and $D$ is the size
of the set of facts.
The complexity proof for the IDE algorithm requires the implementation of the micro-functions
to be \textit{efficient} according to the following criteria:
\begin{enumerate}
	\item There is a representation for the identity and top functions.
  \item The representation is closed under the meet and composition operations.
  \item The micro functions form a finite-height lattice.
  \item The apply, meet, composition, and equality-check operations can be computed in constant time.
  \item There is a constant bound on the storage space for a micro function representation.
\end{enumerate}
We prove that the micro-functions for the correlated-call analysis satisfy these
criteria if we consider the number of correlated-call receivers $R$ and the
number of run-time types $T$ constant
(i.e., the operations on micro-functions are allowed to use time that is $O(RT)$,
but constant with respect to $E$ and $D$).
